Bulk Semantic Annotation with an Partially Known Knowledge Base

### 2024-11-10 doc/sysdesc.tex
more

For this, the author has to be aware that the module from \cref{fig:state-space} exists,
the symbol name, know the URL and manage reduncancy of the imports. At ca 150.000 words in
a semester's words of lecture notes and ca. 10-15\% of technical terms a rather daunting
task.

\sTeX authoring is already supported by an VSCode IDE plugin \cite{sTeX-IDE:git} that
analyzes annotations on the fly, displays the underlying reference semantics, reports
errors and redundancies, and even offers a concept search interface.

>>>>

For this, the author has to be aware ``state space'' is a technical term, that the module
from \cref{fig:state-space} exists, know the symbol name and its URL, and manage
reduncancy of the imports. At ca 150.000 words in a semester's words of lecture notes and
ca. 10-15\% of technical terms a rather daunting task.

\sTeX authoring is already supported by an VSCode IDE plugin \cite{sTeX-IDE:git} that
analyzes annotations on the fly, displays the underlying reference semantics, reports
errors and redundancies, and even offers a concept search interface. But these only offer
support already annotated terms, so they do not solve the annotation problem above.

\section{The \srf System}
